The limits of self commitment and private paternalism \thanks{}

### 2023-01-18 donde.tex
remove soft arms, edit ss, and main table results

Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately. This makes pawn loans a popular way to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.

Pawning is also one of the oldest forms of borrowing. Pawn lending existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}. In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature. The closest product widely studied is payday loans. In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash. According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

As with payday lending, pawnshop lending is controversial. Regulators have concerns with the sophistication of borrowers using it. The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}. The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices. There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%. \cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}   Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.

\subsection{Status Quo Pawn Contracts}

To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple States in Mexico. This lender (whom we refer to as `Lender P') has a simple and typical business model. They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment. No reminders or interim contact exists between the lender and the borrower.  If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece and any payments made. Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.  26\% of borrowers renew at least once with a given pawn. This contract was standard in the industry.

The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).

Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.   One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline our baseline survey at the time they take the loan.  So it does appear that a large share of default is not `planned' in a simple ex-ante sense.  High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return customer. Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, customer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.

Pawnshops therefore make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans. In this way the interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.

\subsection{Measuring the Cost of Pawning} \label{costs}

We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.  The two key measures are loan default, and the effective financial cost incurred by the borrower. Default is defined as losing the pawn. The administrative records show three types of payments made toward recovery of the pawn: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$. We define financial cost according to its default status. Financial cost for default loans is the sum of all payments, and the lost value of the collateral. For recovered loans, financial cost only consists on the sum of interest payments and fees, since payments to principal were allocated to the recovery of the collateral we are not counting it as a cost. Hence the formula for financial cost is :

\begin{align*}
    (\text{Financial Cost})_i =&  \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
\end{align*}

\noindent $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. We also report results using the subjective value of the pawn reported by the borrower in place of the appraised value, and a measure of financial costs that adds travel expenses, since the treatment involves making clients come to the branch to pay each month.

As a second measure of cost we convert that Financial Cost outcome from above to an Annual Percentage Rate (APR). The APR is defined as\footnote{To keep in spirit with the way we are handling incomplete loans, we just say that the loan duration for those is the time that we did observe, so we are adding up all interest and fees over the whole time that loan (including refinancing) has been observed.} :

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}}\right)^{\text{loan duration}}-1 
\end{align*}

We can use the control group for the study to present summary statistics on these core measures of default and financial cost.   Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost, while panel (b) shows the APR. This shows that most of the costs come from clients that do not recover their pawn. 
%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments. It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.\footnote{This fee was set by the lender, being deemed large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.  In contrast with \cite{John} we don't let the clients choose the size of the fee. That paper shows that doing this results in wrong choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment, as explained in the introduction. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
}

As is typical in the behavioral literature we include an arm that allows borrowers to opt in to the commitment contract if they choose.  If, however, a lack of sophistication is an issue with borrowers in pawn contracts, then this process of self-selection may not assign commitment to the `right' people.  To examine this issue, we include an arm  that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.  This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.  This turns out to be key for what we can learn from this experiment.

@@

We did not allocate equal number of days across arms, since we were interested in having more power in some of them. The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.  See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.

@@

 Branch personnel did not know which treatment would happen on which day. They were told that there were 3 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract. They were also told that this way of operating was in place in several of Lender P's branches (they did not know which ones), and that it would be in place for several months. Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs. It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen. Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.

Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has in each arm (rectangles). And for the choice arms, it displays in blue how many people actually chose the respective commitment contract.

For the experiment to be meaningful, it is critical that clients understood the contract terms clearly.  To ensure this, we built two `check-points'.  First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients. One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the reminders and fees associated with the Commitment arm.  Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side). The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms. Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.

The second check-point was that before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}. It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it and asked the client to sign it as a proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.

We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices. As shown below, different contract terms did generate differential demand and differential behavior. Moreover, we can systematically predict demand based on consumer characteristics and measured beliefs.

\subsection{Survey Data and Summary Statistics}

The study exploits two forms of data; administrative data from the lender and a short survey we conducted of experimental clients.

\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns. If I recall correctly, we've settled on including only data for each person's first visit. This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}

The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.

In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e. before treatment status was known). It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.

\subsection{Attrition}

There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment arms.  If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals. We anticipated this possibility and trained appraisers to say that whatever was offered on that day was the only available contract for an undetermined length of time.  Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments. Lender P also never complained to us that our different treatments were hurting sales. The data support this story as well.}

Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active. To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after. We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).  Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.

>>>>

Pawn loans involve individuals leaving valuable liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically larger than the loan, allowing lenders to skip the checking of credit history and give the loan immediately. This makes pawn loans a popular way to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.

Pawning is also one of the oldest forms of borrowing. Pawn lending existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}. In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature. The closest widely studied product is payday loans. In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, making it more accessible to informal sector workers who receive their salaries in cash. %According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

As with payday lending, pawnshop lending is controversial. Regulators have concerns with the sophistication of borrowers using it\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} speculating they may suffer from behavioral and cognitive deficiencies which lead to make sub-optimal choices. There is some evidence in support of this view for payday borrowers.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%. \cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}  Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.

\subsection{Pawning Logistics and Contracts}

To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple States in Mexico. This lender (whom we refer to as `Lender P') has a simple and typical business model.

\paragraph{Appraising and lending.} They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at anytime with no penalty for pre-payment. No reminders or interim contact exists between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made. Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one a (26\% of borrowers renew at least once with a given pawn). This contract was standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).

\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

\subsection{Measuring Borrowers Financial Costs} \label{costs}

Borrowers' financial costs are composed of two main categories: the cost of losing their collateral, and the interest incurred during the life of the loan. For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$) and when. If the client has renewed her loan several times such that the loan is continuing but has not defaulted, we code default as zero. In our data \hl{XX\%} of experimental loans are continuing (i.e. censored) when the data period ends. Regarding interest, the administrative data classifies payments made in three types according to their payment allocation rules: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$. We observe each and every payment made under each category, its amount and date.

We define a borrower's financial cost as the \textcolor{red}{outflow --in cash or pawn value-- from the borrower to the lender.} This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows:

\begin{align*}
    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
\end{align*}

\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. Even though we observe transactions at the day level, \textcolor{red}{we don't use discounting} since the period of loan is only 90 days. \textcolor{red}{In robustness checks we do show that results are virtually unchanged when applying a wide range of time discounting factors.}

We believe the above measure captures financial cost in pesos accurately. However, we will also report results incorporating two costs that are not financial: (i) using the subjective value of the pawn reported by the borrower in place of its appraised gold value, and (ii) adding a measure of travel expenses and the opportunity cost of time, as clients have to go to the branch in order to make payments.

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}. The standard definition is given in the following formula:

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

\vspace{.1in}

Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (\hl{XXX\%}), recovered their pawn (\hl{XXX\%}), or whether they are censored in our data (\hl{XXX\%}). The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost. The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet. Panel (b) shows the APR, which is normalized by loan size; most of the APR costs come from clients that do not recover their pawn. 
%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments. It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was %reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly 
made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

We did not allocate an equal number of days across arms, since we were interested in having more power in some of them. The number of branch days allocated to each were 84 to control, 80 to forced commitment, and 93 to choice. See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.

The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects. One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract. To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment. This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose. This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.

@@

Branch personnel did not know which treatment would happen on which day and were blind to the objective of the intervention. They were told that there were 3 different ``types of contract-days'', that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract. They were also told that this way of operating was in place in several of Lender P's branches (they did not know which ones), and that it would be in place for several months. Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs. It also limits potential manipulation by appraisers, who in the presence of individual-level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen. Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.

%\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns. If I recall correctly, we've settled on including only data for each person's first visit. This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}

Some clients pawned more than one time during the duration of the experiment, with \hl{XXX\%} pawning 2 times and \hl{XXX\%} more than 2 times. To have a clean comparison we are considering only the first pawn in the experiment. It is also the case that \hl{XXX\%} of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted. We treat each of them as separate loans.

\paragraph{Timeline.} Figure \ref{exp_description}(a) \textcolor{red}{shows the timeline when the experiment happens and also the length of time for which we observe payments}. For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery). For contracts in the last week we observe up to \hl{XXX} days, and \hl{XXX\%} of contracts ending observed. Figure \ref{exp_description}(b) shows the number branch-days per arm, the number of contracts, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand them. To ensure this, we built two `check-points'.  First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients. One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the fees associated with the Commitment arm. Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side). The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms. Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings. The second check-point was that before the clients signed the contract, the appraiser made them read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}. It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraiser read it and asked the client to sign it as proof of understating. %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). 
%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}

\subsection{Data}

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. In particular, the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.

\paragraph{Survey data.} In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before treatment status was known to them. The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.

\subsection{Experimental Integrity}
